I/O simulation model with Linux page cache, integration and evaluation in SimGrid framework

### 2020-12-07 paper_io_sim.tex
Update paper text, plotting scripts

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage[dvipsnames]{xcolor}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{ulem}

@@

            \begin{figure}
                   \centering
                   \includegraphics[width=0.85\columnwidth]{figures/interaction.pdf}
                   \caption{Overview of the simulated writeback page cache.
                   Applications send file read or write requests to the
                   IOController that orchestrates flushing, eviction, cache
                   and disk accesses with the MemoryManager. Storage
                   devices (memory and disk) simulate file transfers with
                   bandwidth sharing. \tristan{Could you annotate arrows to
                   make them more explicit?}.}
                   \label{fig:interaction}
            \end{figure}

@@

            Having the model validated, we created simulators for different use cases 
            using WRENCH.
            We implemented our model separately from existing WRENCH components, 
            exposed an API for users, and added an command line argument to enable 
            the model in WRENCH. 
            This helps us to avoid unexpected impacts on WRENCH and 
            independently update the model in the future. 
            We then compared the results of the WRENCH, WRENCH-Ext simulators 
            the results of real execution on a real system.

@@

            The goal of our experiments is to evaluate our page cache 
            simulation in single-threaded and multi-threaded applications
            accessing data on different types of file systems \tristan{"different types" is vague, first thing I thought of was zfs vs ext4 that you don't discuss. Use "local and network" fs instead.}. 
            We use a pipeline
            of sequential tasks where each task reads an input file, increments
            every byte of the input to emulate real processing and avoid caching
            effects \tristan{ambiguous: you're simulating caching effects, you don't want to avoid them. I'd just remove that note and leave "emulate real processing". You could comment on 
            the close-to-zero execution time though, since modeling execution time is out of your scope.}, and writes the result to disk. The output of the previous
            task is the input of the next task. We also use a real application 
            pipeline \textcolor{red}{[Maybe briefly describe this application's purpose (e.g. a standard fMRI preprocessing piepeline)]}, to evaluate the applicability of our simulation model.

            We use a dedicated cluster hosted at Concordia University to conduct 
            the experiments. The cluster consists of one login node, 8 compute nodes \tristan{it now has 9 if you add the GPU node}
            and 4 storage nodes connected with a network bandwidth of 3GBps \tristan{put the Gbps value, 3GBps is unusual as a network bandwidth.}. 
            The login node has one Intel(R) Xeon(R) Gold 6130 CPU @ 2.10GHz, 
            137~GB (128~GiB) of RAM, 1.8TB of storage of XFS file system, 
            13~GB of tmpfs file system and 385 TB of Lustre shared file system \tristan{why do you need to describe the login node in such details?}. 
            Each compute node has two 16 cores Intel(R) Xeon(R) Gold 6130 CPU @ 2.10GHz, 
            275~GB (256~GiB) of RAM and 6 SSDs, 450~GB each with XFS file system, 
            378~GB of tmpfs and 126~GB of devtmpfs file system.
            Lustre file system is configured with one metadata target with 854~GB 
            of storage, 44 object storage targets with 8.7~TB of storage each \tristan{why do we care about Lustre?}. 
            The cluster is run on CentOS 8.1 with NFS version 4. 
            We use \textbf{\textit{atop}} and \textbf{\textit{collectl}} as tools to 
            monitor and collect memory status and disk throughput 
            on the cluster.

            In simulated platform description, because the disk bandwidths in SimGrid 
            are symmetrical, we measure the read/write bandwidths on our cluster and 
            take the average bandwidths. 
            As the pipelines are single-core, we create simulated tasks, 
            each of them runs on only one core. 
            While in Python, computation time can be directly configured, 
            this time is injected to the WRENCH simulators with number of flops, 
            which is calculated with CPU speed and compute duration. 
            In our experiments, the CPU speed is set to 1 Gflops. 
            Finally, because WRENCH simulates applications base on network-communication, 
            we use an infinite bandwidth to eliminate network latency for local I/Os.
            The details of simulated platform and the source code of the simulator 
            are available here: 
            \url{https://github.com/wrench-project/wrench/tree/master/examples/basic-examples/io-pagecache}
            \tristan{Our experiments use commit abcd}

@@

            The pipeline used in this experiment consists of three tasks, 
            each task reads a file, increases every byte and writes output file 
            to local disk. 
            We use the input sizes of 20~GB, 50~GB, 75~GB, 100~GB and run 
            the pipeline on the cluster.
            The pipeline is simulated with the Python prototype simulator, 
            original WRENCH and WRENCH-Ext simulator \tristan{name your simulator something 
            that refers to page cache, maybe WRENCH-cache}.

@@

            Because implementation of a multi-threaded simulator in Python is 
            expensive, and we have our model implemented in WRENCH, 
            we only compare the results of simulators with original WRENCH, 
            WRENCH-Ext and real pipelines in this experiment. 
            The results are compared in total makespan of the pipelines, 
            cumulative read time and cumulative write time.

@@

            We simulate this pipeline with simulators using original WRENCH and 
            WRENCH-Ext. 
            The simulation results are then compared with the real results. 
            Because our work focuses on I/O time, we assume that CPU time is 
            correctly modeled and use the CPU time measured in the real pipelines 
            to setup our simulated workflow. The results are compared in terms of 
            read/write time and total makespan.

    \section{Results}
    \label{results}            
        The benchmark results of bandwidths and the values used in the simulators 
        in our all experiments are shown in Table~\ref{table:benchmark} \tristan{This isn't results, it should go in II.C, 
        next to the paragraph where you talk about symmetrical bandwidths}.

        \begin{table}
        \centering
        \begin{tabular}{|l|c|c|c|}
        \hline
            Bandwidths (MBps)  & Cluster (real) & Python simulator & WRENCH simulator\\
        \hline
            Memory read  & 6860    & 4812     & 4812\\
            Memory write & 2764    & 4812 & 4812\\
            Local disk read & 510 & 465 & 465\\
            Local disk write & 420 & 465     & 465\\
            Remote disk read & 515 & - & 445\\
            Remote disk write & 375 & - & 445\\
            Network bandwidth & 3000 & - & 3000\\
        \hline
        \end{tabular}
        \caption{Bandwidth benchmark results and simulator configurations \tristan{add a sentence of explanation. Make the table fit in 1 column}}
        \label{table:benchmark}
        \end{table}

@@

            Memory behaviors of real pipeline execution and simulators are recorded 
            and the memory profiling results with 20GB and 100GB input files 
            are illustrated in Figure~\ref{fig:single_memprof} \tristan{convoluted writing}. 
            The bars in the figures present activities in tasks (read, compute and write), 
            while the lines describe memory status throughout run time of the pipeline \tristan{move any description of graphical features to the figure caption}. 
            Because the results with 20Gb, 50GB, 100GB are analogous, we only include 
            the results with 20GB and 100GB in this paper \tristan{analogous is not the right word}.

            As shown in the figures, the makespans of the simulated pipeline are 
            close to the makespan of the real execution with similar patterns of I/O time 
            real execution and simulation. 
            But more importantly, with all input sizes, similar trends can also be found 
            in the lines describing memory status in simulators and the real execution. 
            The similar evolutions of amount of cache used (purple lines) in reality 
            and simulation show that the use of page cache is well reproduced by the simulators. 
            The amount of dirty data ( red lines) also follow similar trends, 
            which means not only the amount dirty data, but also the flushing and 
            periodical flushing mechanisms are accurately modeled in our simulators. 
            This can be seen in in the increase of the amount of dirty data during the writes 
            and the decrease during the reads and computations. 
            According to the results achieved with all input sizes in the experiment, 
            we can observe identical trends in reality and simulation with 20GB, 
            50GB and 75GB input files. However, with 100GB input file, 
            the third read is not correctly simulated, leading to longer simulated time 
            than in real execution. This will be explained later in this section.

            The I/O time of tasks in simulators and real execution is also tracked and compared. 
            Figure~\ref{fig:single_errors} \tristan{wrong reference} shows the relative error of simulated I/O time 
            of individual I/O activities. 
            Our pipeline consists of 3 tasks, and each task reads an input file, 
            performs some computation, and writes output file. 
            Thus, there are 6 sequential I/O activities, \textit{Read 1} and \textit{Write 1} 
            from the first task, \textit{Read 2} and \textit{Write 2} the second task, 
            and \textit{Read 3}, \textit{Write3} from the last task.

            In general, with all input sizes in the experiment, the simulation errors 
            of simulators with page cache model (Python and WRENCH-Ext simulators) 
            are remarkably lower than the result with original WRENCH . 
            The reason is, in original WRENCH, because page cache is not simulated, 
            data is only read/written with disk bandwidth, which is much slower 
            than memory bandwidths, leading to simulated I/O time longer than in reality.
            Especially, the simulation time errors of \textit{Read 3} in the simulators 
            with page cache are just under the error in original WRENCH.

            \begin{figure*}
            \centering
            \begin{subfigure}{\linewidth}
                \centering
                   \includegraphics[width=\linewidth]{result/single/figures/single_memprof.pdf}
            \end{subfigure}
            \caption{Memory profiling results with different input file sizes \tristan{put the simulation/real conditions on the side, make them larger and use the same color code as below (pink for real, etc). Put the memory values on top, similar to how they are in the graphs below. }}
            \label{fig:single_memprof}    
            \begin{subfigure}{\linewidth}
                \centering
                   \includegraphics[width=\linewidth]{result/single/figures/single_errors.pdf}
            \end{subfigure}
            \caption{Simulation errors with different input file sizes}
            \label{fig:single_error}    
            \begin{subfigure}{\linewidth}
                \centering
                   \includegraphics[width=\linewidth]{result/single/figures/cached_files.pdf}
            \end{subfigure}    
            \label{fig:single_cache}
               \caption{Amount of file data in cache after each I/O activity with 100GB of input \tristan{Make a grouped histogram (1 histogram with two bars, one for real, one for simulation). Add a grouped histogram for 20GB. Use the same color code everywhere: real should be pink.}}
            \end{figure*}

            This longer read can be explained with the amount of cached data of files 
            at the beginning of the read in reality and simulators shown in 
            Figure~\ref{fig:single_cache}.             
            In this figure, \textit{file $<$i$>$} is the input of \textit{Read $<$i$>$} and 
            output of \textit{Write $<$i-1$>$}. 
            In the real execution, after \textit{Write 2}, which writes \textit{file 3}, 
            all data of \textit{file 3} is in cache. 
            Thus, in \textit{Read 3}, \textit{file 3} is read with memory bandwidth. 
            But in our simulator, after \textit{Write 2}, only a part of \textit{file 3} 
            remains in cache. 
            The reason is while \textit{file 3}  is being written, the page cache is saturated, 
            eviction is then evoked to evict data from page cache, make space 
            available for \textit{file 3}. 
            However, because the evicted amount is less than required, 
            some \textit{file 3} data is evicted after being written, make \textit{file 3} 
            partially cached. 
            As a result, in \textit{Read 3}, only a part of \textit{file 3} is read from cache 
            with memory bandwidth, a part of it is read from disk with disk read bandwidth, 
            which is many times slower, leading to longer read time.

@@

            \begin{figure*}        
            \begin{subfigure}{\linewidth}
                \centering
                   \includegraphics[width=\linewidth]{result/multi/figures/multi_local.pdf}
            \end{subfigure}        
            \caption{I/O time of concurrent pipelines with local storage. \tristan{revise caption for real execution variability: "real execution" doesnt tell what the gray shade is.}}
            \label{fig:multi_local}
            \end{figure*}

            In this experiment, the results are analyzed in terms of average I/O time 
            of concurrent pipelines shown in Figure~\ref{fig:multi_local}.

            As is shown in the figure, when the number of pipelines increases, 
            the average read time raises accordingly because the amount of data 
            increases but memory and disk bandwidths are fixed and shared between pipelines. 
            In comparison with original WRENCH, the results from WRENCH-Ext are closer 
            to reality. 
            Especially, when it comes to the average write time, 
            although the trend in reality is more complex, our WRENCH-Ext 
            simulator can still capture the pattern in real execution.
            In both, the average write time gradually increases before surging with the 
            same slopes after the number of pipelines reaches 10. 
            This can be explained that with less than 10 concurrent pipelines, 
            the page cache is not saturated, so all files can be written entirely to 
            cache with memory bandwidth in a short time. 
            After the page cache is saturated with dirty data (at around 
            10 concurrent pipelines in this experiment), this dirty data needs 
            to be flushed in order to make space available for writing new data to cache. 
            This dirty data is flushed to disk with disk bandwidth, which is much  
            slower than memory bandwidth. 
            The more pipelines we have, the more data needs to be written, the more data 
            needs to be flushed, leading to a sharper increase in the average write time.

            To conclude, the results from WRENCH-Ext simulator show that 
            our model can also simulate I/O with page cache accurately in a 
            multi-threaded application.

@@

            Similarly, the results with from the experiment with NFS are described 
            by the average I/O time shown in Figure~\ref{fig:multi_nfs}.
            In general, the average I/O time reflect a very similar level of accuracy 
            to the previous experiment results when the I/O time of pipelines 
            is very close to the real execution. 
            The simulated read time if a bit off when the number of pipelines 
            surpasses 22, with 264 GB of data in total. 
            This is due to the impact of simulated cache eviction when 
            the page cache is saturated, which has been seen in 
            Figure~\ref{fig:single_error} with 100 GB of input. 
            When it comes to write time, original WRENCH and WRENCH-Ext 
            results are identical when both are writing directly to disk.

@@

    \section{Discussion and Future Work}
    \label{discussion}            
            In computing infrastructures, especially those use for data-intensive applications, 
            page cache undoubtedly has certain impacts on performance. 
            Conducting simulation experiments is an effective approach to predict, 
            evaluate the performance of not only application, scheduler but also 
            infrastructure settings. 
            Unfortunately, page cache is missing in many simulation tools for HPC systems. 
            In this study, we proposed a simulation model of I/O with page cache, 
            implement it with SimGrid using WRENCH, and evaluate the results 
            with different experiments. 
            The results shows our achievements in terms of simulation accuracy 
            and the application potential in practice \tristan{what do you conclude? can we use your simulator to study big data applications on hpc clusters? under what conditions?}. 
            On the other hands, the model exposed some limitations that can be 
            further improved.

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage[dvipsnames]{xcolor}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{ulem}
\usepackage{tabularx}

@@

            \begin{figure}
                \centering
                \includegraphics[width=0.85\columnwidth]{figures/interaction.pdf}
                   \caption{Overview of the simulated writeback page cache.
                   Application sends file read and file write requests to IOController,
                   then IOController manages orchestrate flushing, eviction, cache and
                   disk accesses to fulfill the requests with the MemoryManager object.
                   Memory and Disk are responsible for simulating I/O time.}
                   \label{fig:interaction}
            \end{figure}

@@

            Having the model validated, we created simulators for different use cases
            using WRENCH.
            We implemented our model separately from existing WRENCH components,
            exposed an API for users, and added an command line argument to enable
            the model in WRENCH.
            This helps us to avoid unexpected impacts on WRENCH and
            independently update the model in the future.
            We then compared the results of the WRENCH, WRENCH-cache simulators
            the results of real execution on a real system.

@@

            The goal of our experiments is to evaluate our page cache
            simulation in single-threaded and multi-threaded applications
            accessing data on local and network file systems.
            We use a pipeline of sequential tasks where each task reads an input file,
            increments every byte of the input to emulate real processing, and writes
            the result to disk.
            The output of the previous task is the input of the next task.
            We also use a real application pipeline \textcolor{red}{[Maybe briefly describe this application's purpose (e.g. a standard fMRI preprocessing piepeline)]},
            to evaluate the applicability of our simulation model.

            We use a dedicated cluster hosted at Concordia University to conduct
            the experiments. The cluster consists of one login node, 9 compute nodes
            and 4 storage nodes connected with a network bandwidth of 25 Gbps.
            Each compute node has two 16 cores Intel(R) Xeon(R) Gold 6130 CPU @ 2.10GHz,
            275~GB (256~GiB) of RAM and 6 SSDs, 450~GB each with XFS file system,
            378~GB of tmpfs and 126~GB of devtmpfs file system.
            The cluster is run on CentOS 8.1 with NFS version 4.
            We use \textbf{\textit{atop}} and \textbf{\textit{collectl}} as tools to
            monitor and collect memory status and disk throughput
            on the cluster.

            In simulated platform description, because the disk bandwidths in SimGrid
            are symmetrical, we measure the read/write bandwidths on our cluster and
            take the average bandwidths.
            The benchmark results of bandwidths and the values used in the simulators
            in our all experiments are shown in Table~\ref{table:benchmark}.

            \begin{table}[htbp]
            \centering
            \begin{tabularx}{\columnwidth}{|l
            |>{\centering\arraybackslash}X
            |>{\centering\arraybackslash}X
            |>{\centering\arraybackslash}X|}
            \hline
                Bandwidths (MBps)  & Cluster (real) & Python simulator & WRENCH simulator\\
            \hline
                Memory read  & 6860	& 4812	 & 4812\\
                Memory write & 2764	& 4812 & 4812\\
                Local disk read & 510 & 465 & 465\\
                Local disk write & 420 & 465	 & 465\\
                Remote disk read & 515 & - & 445\\
                Remote disk write & 375 & - & 445\\
                Network bandwidth & 3000 & - & 3000\\
            \hline
            \end{tabularx}
            \caption{Bandwidth benchmark results and simulator configurations.
            The bandwidths used in simulators are average of read and write bandwidths
            measured on the cluster.
            Remote disk and network are not simulated in Python simulator.}
            \label{table:benchmark}
            \end{table}

            As the pipelines are single-core, we create simulated tasks,
            each of them runs on only one core.
            While in Python, computation time can be directly configured,
            this time is injected to the WRENCH simulators with number of flops,
            which is calculated with CPU speed and compute duration.
            In our experiments, the CPU speed is set to 1 Gflops.
            Finally, because WRENCH simulates applications base on network-communication,
            we use an infinite bandwidth to eliminate network latency for local I/Os.
            The details of simulated platform and the source code of the simulator
            used in our experiments are available in this commit:
            \url{https://github.com/wrench-project/wrench/tree/ec6b43561b95977002258c0fe37a4ecad8f1d33f/examples/basic-examples/io-pagecache}.

@@

            The pipeline used in this experiment consists of three tasks,
            each task reads a file, increases every byte and writes output file
            to local disk.
            We use the input sizes of 20~GB, 50~GB, 75~GB, 100~GB and run
            the pipeline on the cluster.
            The pipeline is simulated with the Python prototype simulator,
            original WRENCH and WRENCH-cache simulator.

@@

            Because implementation of a multi-threaded simulator in Python is 
            expensive, and we have our model implemented in WRENCH, 
            we only compare the results of simulators with original WRENCH, 
            WRENCH-cache and real pipelines in this experiment. 
            The results are compared in total makespan of the pipelines, 
            cumulative read time and cumulative write time.

@@

            We simulate this pipeline with simulators using original WRENCH and 
            WRENCH-cache. 
            The simulation results are then compared with the real results. 
            Because our work focuses on I/O time, we assume that CPU time is 
            correctly modeled and use the CPU time measured in the real pipelines 
            to setup our simulated workflow. The results are compared in terms of 
            read/write time and total makespan.

    \section{Results}
    \label{results}

@@

            Memory profiling results of real pipeline execution and simulators 
			with 20GB and 100GB input files are illustrated in Fig.~\ref{fig:single_memprof}.
			Because the results with 20Gb, 50GB, 100GB shows a similar pattern,
			we only include the results with 20GB and 100GB in this paper.

			As shown in the figures, the makespans of the simulated pipeline are
			close to the makespan of the real execution with similar patterns of I/O time
			real execution and simulation.
			But more importantly, with all input sizes, similar trends can also be found
			in the lines describing memory status in simulators and the real execution.
			The similar evolutions of amount of cache used (purple lines) in reality
			and simulation show that the use of page cache is well reproduced by the simulators.
			The amount of dirty data (red lines) also follow similar trends,
			which means not only the amount dirty data, but also the flushing and
			periodical flushing mechanisms are accurately modeled in our simulators.
			This can be seen in in the increase of the amount of dirty data during the writes
			and the decrease during the reads and computations.
			According to the results achieved with all input sizes in the experiment,
			we can observe identical trends in reality and simulation with 20GB,
			50GB and 75GB input files. However, with 100GB input file,
			the third read is not correctly simulated, leading to longer simulated time
			than in real execution. This will be explained later in this section.

			The I/O time of tasks in simulators and real execution is also tracked and compared.
			Fig.~\ref{fig:single_error} shows the relative error of simulated I/O time
			of individual I/O activities.
			Our pipeline consists of 3 tasks, and each task reads an input file,
			performs some computation, and writes output file.
			Thus, there are 6 sequential I/O activities, \textit{Read 1} and \textit{Write 1}
			from the first task, \textit{Read 2} and \textit{Write 2} the second task,
			and \textit{Read 3}, \textit{Write3} from the last task.

			\begin{figure*}
			\centering
			\begin{subfigure}{\linewidth}
				\centering
   				\includegraphics[width=\linewidth]{result/single/figures/single_memprof.pdf}
			\end{subfigure}
			\caption{Memory profiling results with different input file sizes.
			The bars in the figures present activities in tasks (read, compute and write),
			the lines describe memory status throughout run time of the pipeline.}
			\label{fig:single_memprof}
			\begin{subfigure}{\linewidth}
				\centering
   				\includegraphics[width=\linewidth]{result/single/figures/single_errors.pdf}
			\end{subfigure}
			\caption{Simulation errors with different input file sizes}
			\label{fig:single_error}
			\begin{subfigure}{\linewidth}
				\centering
   				\includegraphics[width=\linewidth]{result/single/figures/cached_files.pdf}
			\end{subfigure}
			\label{fig:single_cache}
   			\caption{Amount of file data in cache after each I/O operation. 
   			\textcolor{red}{Update real results of 20GB}}
			\end{figure*}

			In general, with all input sizes in the experiment, the simulation errors
			of simulators with page cache model (Python and WRENCH-cache simulators)
			are remarkably lower than the result with original WRENCH .
			The reason is, in original WRENCH, because page cache is not simulated,
			data is only read and written with disk bandwidth, which is much slower
			than memory bandwidths, leading to simulated I/O time longer than in reality.
			Especially, the simulation time errors of \textit{Read 3} with 100 GB of input
			in the simulators with page cache are just under the error in original WRENCH.
			This longer read can be explained with the amount of cached data of files
			at the beginning of the read in reality and simulators shown in
			Fig.~\ref{fig:single_cache}.
			In this figure, \textit{file $<$i$>$} is the input of \textit{Read $<$i$>$} and
			output of \textit{Write $<$i-1$>$}.
			With the input size of 20 GB, in both real execution and WRENCH-cache
			simulator, there is no difference in the page cache since all files in the
			pipeline can be entirely cached.
			With the input of 100 GB, the difference between real execution and WRENCH-cache
			simulator can be seen in the amount of \textit{file 3} cache after \textit{Write 2}.
			In real execution, after being written by \textit{Write 2},
			\textit{file 3} is entirely in cache.
			Thus, in \textit{Read 3}, \textit{file 3} is read with memory bandwidth.
			However, in the WRENCH-cache simulator, only a part of \textit{file 3} is
			cached after \textit{Write 2}, which means \textit{Write 2} reads a part of
			\textit{file 3} from disk.
			The reason for the difference is in our WRENCH-cache simulator,
			with 100 GB of input, while \textit{file 3} is being written,
			the page cache is saturated, eviction is then evoked to evict data
			from page cache and make space available for \textit{file 3}.
			However, because the evicted amount is less than required,
			some \textit{file 3} data is evicted after being written, make \textit{file 3}
			partially cached.
			As a result, in \textit{Read 3}, only a part of \textit{file 3} is read from cache
			with memory bandwidth, a part of it is read from disk with disk read bandwidth,
			which is many times slower, leading to longer read time.

@@

            \begin{figure*}
            \begin{subfigure}{\linewidth}
                \centering
                \includegraphics[width=\linewidth]{result/multi/figures/multi_local.pdf}
            \end{subfigure}
            \caption{I/O time of concurrent pipelines with local storage.}
            \label{fig:multi_local}
            \end{figure*}

            In this experiment, we run the real execution in 5 repetitions to
            capture the variability on the cluster.
            The results are analyzed in terms of average I/O time
            of concurrent pipelines shown in Fig.~\ref{fig:multi_local}.

            As is shown in the figure, when the number of pipelines increases,
            the average read time raises accordingly because the amount of data
            increases but memory and disk bandwidths are fixed and shared between pipelines.
            In comparison with original WRENCH, the results from WRENCH-cache are closer
            to reality.
            Especially, when it comes to the average write time,
            although the trend in reality is more complex, our WRENCH-cache
            simulator can still capture the pattern in real execution.
            In both, the average write time gradually increases before surging with the
            same slopes after the number of pipelines reaches 10.
            This can be explained that with less than 10 concurrent pipelines,
            the page cache is not saturated, so all files can be written entirely to
            cache with memory bandwidth in a short time.
            After the page cache is saturated with dirty data (at around
            10 concurrent pipelines in this experiment), this dirty data needs
            to be flushed in order to make space available for writing new data to cache.
            This dirty data is flushed to disk with disk bandwidth, which is much
            slower than memory bandwidth.
            The more pipelines we have, the more data needs to be written, the more data
            needs to be flushed, leading to a sharper increase in the average write time.

            To conclude, the results from WRENCH-cache simulator show that
            our model can also simulate I/O with page cache accurately in a
            multi-threaded application.

@@

            Similar to the previous experiment, the real execution with NFS is also
            repeated for 5 times and the results are described with the average I/O time
            shown in Fig.~\ref{fig:multi_nfs}.
            In general, the average I/O time reflect a very similar level of accuracy
            to the previous experiment results when the I/O time of pipelines
            is very close to the real execution.
            The simulated read time if a bit off when the number of pipelines
            surpasses 22, with 264 GB of data in total.
            This is due to the impact of simulated cache eviction when
            the page cache is saturated, which has been seen in
            Fig.~\ref{fig:single_error} with 100 GB of input.
            When it comes to write time, original WRENCH and WRENCH-cache
            results are identical when both are writing directly to disk.

@@

    \section{Discussion and Future Work}
    \label{discussion}
        In computing infrastructures, especially those use for data-intensive applications,
        page cache undoubtedly has certain impacts on performance.
        Conducting simulation experiments is an effective approach to predict,
        evaluate the performance of not only application, scheduler but also
        infrastructure settings.
        Unfortunately, page cache is missing in many simulation tools for HPC systems.
        In this study, we proposed a simulation model of I/O with page cache,
        implement it with SimGrid using WRENCH, and evaluate the results
        with different experiments.
        The results shows that our model can result in better simulation accuracy than
        the simulators in which page cache is not modeled.
        Furthermore, this level of accuracy can be achieved without a fine-grained
        level of details.
        This may create opportunities for the model to be applied in simulation of
        big data applications on HPC infrastructures, which leverage memory to
        employ page cache as a disk cache.
        Nevertheless, the model exposed some limitations that can be
        further improved.
